working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-11 Manuscript_draft/Manuscript_draft.tex
edits

\begin{figure}
\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae.}\label{fig:unnamed-chunk-1}
\end{figure}

@@

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and across families, see
\textbf{Figure 2}. Despite some variability in the effect of the
different pollen donors per species, in general terms the effect of
heterospecific pollen from the distinct nine treatments per species was
homogeneous (see \textbf{Figure 3}), just for four species out of ten,
just one donor did not overlap the confidence intervals with other
donors. Therefore, none of the donors had a clear stronger or weaker
effect across species. When the donors were groped by family not big
differences were seen, just for \emph{S. lycopersicum} the confidence
intervals of Brassicaceae and Convolvulaceae did not overlap (see
\textbf{Figure 4}). In addition, for the 100\% hetrospecific pollen
treatments we did not find almost seed production. However, for just one
species (\emph{S. alba}) the control pollination and the heterospecific
pollination with pollen from a confamilial had similar seed production.
For both Solanaceae species \emph{S. melongena} and \emph{C. annuum}
100\% pollen treatments produced few seedles fruits (3\% and 9\%
respectively) and they did not for the apomictic treatments.

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a positive statistically clear correlation
for both markers (p\textless{}0.05). The correlations with ITS and RBCL
markers was respectively of 0.29 and 0.25. The phylogenetic signal of
traits was significantly correlated with pollen size, stigma
measurements and style length (p\textless{}0.05). Although with a lack
of a significant correlation pagel's lambda values were also relatively
high (\textgreater{}0.45) for incompatibility index, ovary length and
levels of selfing. Moreover, Mantel test between heterospecific pollen
effect and traits gave also a positive significant correlation with a r
value of 0.4. When the effect was look trait by trait with Mantel test,
stigma type and stigma measurements (length, width and area) gave a
significant positive correlation with heterospecific pollen effect (LOOK
AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE
OPPOSITE)

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae}\label{fig:unnamed-chunk-1}
\end{figure}

@@

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and across families, see
\textbf{Figure 2}. Despite some variability in the effect of the
different pollen donors per species, in general terms the effect of
heterospecific pollen from the distinct nine treatments per species was
homogeneous (see \textbf{Figure 3}), just for four species out of ten,
just one donor did not overlap the confidence intervals with other
donors. Therefore, none of the donors had a clear stronger or weaker
effect across species. When the donors were groped by family not big
differences were seen, just for \emph{S. lycopersicum} the confidence
intervals of Brassicaceae and Convolvulaceae did not overlap (see
\textbf{Figure 4}). In addition, for the 100\% hetrospecific pollen
treatments we did not find almost seed production. However, for just one
species (\emph{S. alba}) the control pollination and the heterospecific
pollination with pollen from a confamilial had similar seed production.
For two Solanaceae species \emph{S. melongena} and \emph{C. annuum}
100\% pollen treatments produced few seedles fruits (3\% and 9\%
respectively) and they did not for the apomictic treatments.

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a positive statistically clear correlation
for both markers (p\textless{}0.05). The correlations with ITS and RBCL
markers was respectively of 0.29 and 0.25. We found a significant
phylogenetic signal of traits for pollen size, stigma measurements and
style length (p\textless{}0.05). Although with a lack of a significant
correlation pagel's lambda values were also relatively high
(\textgreater{}0.45) for incompatibility index, ovary length and levels
of selfing. Moreover, Mantel test between heterospecific pollen effect
and traits gave also a positive significant correlation with a r value
of 0.4. When the effect was look trait by trait with Mantel test, stigma
type and stigma measurements (length, width and area) gave a significant
positive correlation with heterospecific pollen effect.
